Automated topic naming to support analysis of software maintenance activities

### 2010-08-20 icse/icse2011.tex
analysis of supervised labelling edits

\subsubsection{Analysis of the supervised labelling}
\label{sec:suplabelling}
Because our data-set was of word counts we expected Bayesian techniques, often used in spam filtering, to perform well. We tried other learners that WEKA~\cite{weka09} provides: rule learners, decision tree learners, vector space learners, and support vector machines.  Figure \ref{fig:best-learn-per-tag} shows the performance of the best performing learner per label.  We considered the best learner for a label to be the one which had the highest ROC value for that label. Figure \ref{fig:best-learn-per-tag} uses the ZeroR learner as a baseline, a common practice in machine learning. ZeroR naively chooses the largest category all of the time. It occasionally outperforms non-naive learners; for labels which are not as common, this is to be expected because any miscategorization will hurt accuracy. This is why we use ROC values, as they can better represent performance on labels which are not applicable to the majority of samples.

@@

The less-frequently occurring a label the harder it is to get accurate
results, due to the high noise level. Nevertheless, these results are
better than our previous word bag results of \textsf{exp2} and
\textsf{exp3}, because the ROC values are sufficiently higher in most
cases (other than MaxDB \emph{reliability} and MySQL \emph{efficiency}). The
limitation of the approach we took here is that we assume labels are
independent; however, labels could be correlated with each other. 
The next section, Section \ref{sec:multilabel} on multi-labels
addresses the issue of a lack of independence and correlation between labels.
In the next section we will evaluate how well these learners perform
together.
%\todo[inline]{Comment about correlation, we should link to the Mulan section, perfect segway since Mulan relies on correlation.}

>>>>

\subsubsection{Analysis of the supervised labelling}
\label{sec:suplabelling}
Because our data-set was of word counts we expected Bayesian techniques, often used in spam filtering, to perform well. 
We tried other learners that WEKA~\cite{weka09} provides: rule learners, decision tree learners, vector space learners, and support vector machines.  
Figure \ref{fig:best-learn-per-tag} shows the performance of the best performing learner per label. 
 We considered the best learner for a label to be the learner which had the highest ROC value for that label. 
Figure \ref{fig:best-learn-per-tag} uses the ZeroR learner as a baseline, a common practice in machine learning,
as ZeroR naively chooses the largest category all of the time. 
ZeroR occasionally outperforms other learners; for labels which are not as common, this is to be expected because any miscategorization will hurt accuracy. 
This is why we use ROC values, instead of accuracy, as they can better represent performance on labels which are not applicable to the majority of samples.

@@

The less-frequently occurring a label, the harder it is to get accurate
results, due to the high noise level. Nevertheless, these results are
better than our previous word bag results of \textsf{exp2} and
\textsf{exp3}, because the ROC values are sufficiently higher in most
cases (other than MaxDB \emph{reliability} and MySQL \emph{efficiency}). The
limitation of the approach we took here is that we assume labels are
independent; however, labels could be correlated with each other. 
The next section, Section \ref{sec:multilabel} on multi-labels
addresses the issue of a lack of independence and correlation between labels.
In the next section we will evaluate how well these learners perform
together.
%\todo[inline]{Comment about correlation, we should link to the Mulan section, perfect segway since Mulan relies on correlation.}
